\documentclass{article}
\author{The Contributors}
\title{My Glimpse Of Propositional Logic Inside The Ivory Tower Of
  Mathematics}
  \usepackage[tex4ht]{hyperref}
\begin{document}
  \maketitle
  \tableofcontents

  \section{Introduction}

  I'm a mathematical barbarian, but a few days ago I broke into the ivory tower
  of mathematics and learnt the basics of Propositional Logic. In order to help
  me learn it, I wrote this tutorial. It helped me, and perhaps you'll find it
  useful too.

  \subsection{Licence}

    This work is licensed under a
    \href{http://creativecommons.org/licenses/by-sa/4.0/}{Creative Commons
    Attribution-ShareAlike 4.0 International License}.

  \subsection{Contributing}

    All contributions (corrections, amendments, additions etc) welcome at
    \url{https://github.com/tlocke/maths}.


  \section{\label{sec:propositions}Propositions}

    In propositional logic, we're only interested in sentences that are either
    true or false. Such sentences are known as \emph{propositions}. Here are
    some sentences together with explanations of whether they are propositions
    or not:

    \begin{itemize}

      \item \emph{How many miles to Crinnis?}

        This is a question, so not a proposition.

      \item \emph{Elephants have four legs.}

        Yay, an actual proposition! It's a sentence that is either true or
        false.

      \item \emph{Don't dilly-dally.}

        This isn't true or false, it sounds like someone admonishing somebody.
        Not a proposition.

      \item \emph{The capital of France is Paris.}

        Yes, a proposition.

      \item \emph{He likes chocolate.}

        This sounds like a proposition, but according to those logicians in
        the ivory tower it doesn't count because it relies on knowing who `he'
        is.

      \item \emph{Don't spoil the ship for a ha'peth of tar.}

        This is a proverb, not a proposition.

    \end{itemize}

    I've got this nagging doubt in my mind. Most propositions I can think of
    aren't \emph{totally} ambiguous. Take the `Elephants have four legs'
    example. Maybe there's a three legged elephant in existence, perhaps one in
    a zoo got gangrene or something and had to have a leg amputated \ldots
    Nevertheless, let's suspend our disbelief and imagine all those perfect
    propositions.

    \subsection*{Questions}

      \begin{enumerate} 

        \item Which of the following are propositions?
          \begin{enumerate}
            \item Who is John Galt?
            \item He's over there.
            \item Three divided by three is one.
            \item Belgium is a European country.
            \item Praise be!
            \item Blue is a colour.
          \end{enumerate}

        \item Are the following propositions true or false?
          \begin{enumerate}
            \item Four is greater than two.
            \item Tennis is a colour.
            \item A square has eight sides.
            \item A cube has eight corners.
            \item Birmingham is a city in England.
            \item The word `rotavator' is a
              \href{http://en.wiktionary.org/wiki/palindrome}{palindrome}.
          \end{enumerate}

      \end{enumerate}

  \section{\label{sec:expressions}Expressions}

    It seems that the next thing the logicians do is string together
    propositions. They call the result an \emph{expression}. So two
    propositions might be:

    \begin{itemize}
      \item Abelard likes coffee.
      \item Abelard likes cake.
    \end{itemize}

    And an expression formed from these propositions might be:

    \begin{quote}
      \item Abelard likes coffee and Abelard likes cake.
    \end{quote}

    This expression is true if both the propositions are true, otherwise it is
    false. Another expression we can make from our propositions is:

    \begin{quote}
      \item Abelard likes coffee or Abelard likes cake.
    \end{quote}

    This expression is false if both propositions are false, otherwise it's
    true. Those mathematicians from the Ivory Tower use the term
    \emph{connectives} for the `and' and `or' that join propositions to make
    expressions.

    \subsection*{Questions}

      \begin{enumerate} 

        \item Are the following expressions true or false?
          \begin{enumerate}
            \item The film Erin Brokovich stars Julia Roberts and 16 is greater
              than 4.
            \item London is the capital of France or Paris is the capital of
              France.
            \item Some people have brown eyes and humans lay eggs.
            \item Four multiplied by two is twenty or it has never rained in
              Wales.
            \item Toothpaste is harder than diamond and less than 100 films
              have ever been made.
          \end{enumerate}

      \end{enumerate}

  \section{\label{sec:labels}Labels}

    Rather than always writing propositions out in full, those work-shy
    logicians assign a label to them. So for the expression:

    \begin{itemize}



  \section{Rosetta Stone}

    \begin{itemize}
      \item Expression - Formula, Compound Proposition
    \end{itemize}
  \appendix
  \section{Answers To Section Questions}

  \subsection*{\ref{sec:propositions} Propositions}

      \begin{enumerate} 
        \item
          \begin{enumerate}
            \item Not a proposition.
            \item Not a proposition.
            \item A proposition.
            \item A proposition.
            \item Not a proposition.
            \item A proposition.
          \end{enumerate}
        \item
          \begin{enumerate}
            \item True.
            \item False.
            \item False.
            \item True.
            \item True.
            \item True.
          \end{enumerate}
      \end{enumerate}

  \subsection*{\ref{sec:expressions} Expressions}

      \begin{enumerate} 
        \item
          \begin{enumerate}
            \item True.
            \item True.
            \item False.
            \item False.
            \item False.
          \end{enumerate}
      \end{enumerate}
\end{document}
